---
title: "TCGA Cancer Genomic Analysis using R"
author: "Jun Kang"
date: '2019 5 17 '
output:
  beamer_presentation: 
    colortheme: orchid
    fig_height: 4
    fonttheme: professionalfonts
    highlight: espresso
    keep_tex: yes
    theme: CambridgeUS
header-includes:
- \usepackage{graphicx}
- \usepackage{tikzpagenodes}
- \usetikzlibrary{calc}
- \usepackage{caption}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(tinytex.verbose = TRUE)
```

## The Cancer Genome Atlas (TCGA)

- Landmark cancer genomics program
- Over 20,000 primary cancer and matched normal samples spanning 33 cancer types
- 2.5 petabytes of genomic, epigenomic, transcriptomic, and proteomic data
- Publicly available for anyone in the research community to use
- https://www.cancer.gov/about-nci/organization/ccg/research/structural-genomics/tcga

## TCGA genomic data

- R and Rstudio
- **RTCGAToolbox** package
- **cgdsr** package

## Slide with R Output

```{r RTCGAToolbox, echo = TRUE}
library('RTCGAToolbox')
getFirehoseDatasets()
getFirehoseRunningDates(last = NULL)
```

## Read Data from Firehose
```{r readData, echo=TRUE, message=FALSE, cache=TRUE}
readData = getFirehoseData (dataset="BRCA", 
                            runDate="20160128",
                            forceDownload = TRUE,
                            Clinic=TRUE, 
                            RNASeq2GeneNorm=TRUE)
```

## Get clinical data
```{r clinical data, echo=TRUE}
clin <- getData(readData, "clinical")
clin[1:2,1:2]
```

## Get mesengerRNA expresion data
```{r mRNA, echo=TRUE, cache=TRUE}
mRNA <- t(getData(readData, 'RNASeq2GeneNorm'))
mRNA[1:2, 1:2]
```


## cgdsr
- cbioportal https://www.cbioportal.org/
```{r cgdsr, echo=TRUE, message=FALSE}
library(cgdsr)
# Create CGDS object
mycgds = CGDS("https://www.cbioportal.org/")

# Get list of cancer studies at server
getCancerStudies(mycgds)[1:2,]
```
## GDC Data Portal
- https://portal.gdc.cancer.gov/


## Comprehensive research 
- https://wiki.cancerimagingarchive.net/pages/viewpage.action?pageId=33948919

## Comprehensive research
```{r til plot, echo=TRUE, message=FALSE, warning=FALSE}
Til_map <- read.delim('TILMap_TableS1.txt')
library(dplyr)
library(ggplot2)
ggplot(Til_map, aes(x=Study, y=Leukocyte.Fraction)) +
         geom_boxplot()
```

## SessionInfo
```{r sessionInfo, echo=TRUE}
library(pander)
pander(sessionInfo())
```